---
title: "STAT 33B Lab 3"
author: "Ziang Gao (3033669851)"
output: pdf_document
---

Edit this file, knit to PDF, and:

* Submit the Rmd file on bCourses.
* Submit the PDF file on Gradescope.

If you think you'll need help with submission, please ask during the lab.

Answer all questions with complete sentences, and put code in code chunks. You
can make as many new code chunks as you like. Please do not delete the
exercises already in this notebook, because it may interfere with our grading
tools.

As you work, you may find it helpful to be able to run your code. You can run a
single line of code by pressing Ctrl + Enter. You can run an entire code chunk
by clicking on the green arrow in the upper right corner of the code chunk. 

Knit the document from time to time to make sure that your code runs without
errors from top to bottom in a fresh R environment. 

The code below controls the number of significant digits shown for the return
values in your knitted document.

```{r}
options(digits = 3)
```

Datasaurus Dozen Data Set
=========================

Exercise 1 uses the Datasaurus Dozen Data Set from homework 2.


Exercise 1
----------

A "faceted" plot is one that shows several plots side-by-side, to aid
comparison between them. Each subplot is called a "facet".

You can create a faceted plot with `ggplot2` by using the facet layer. For
instance, the `facet_wrap()` function creates a line of facets based on a
single categorical variable. The facet layer should be added to a plot _after_
the geometry layers.

1.  Read the documentation for `facet_wrap()`, then create a faceted scatter
    plot that shows each dataset from the Datasaurus Dozen in a separate facet.
    Use `geom_smooth` with `method = "lm"` to add a linear regression line to
    each facet.

    _Hint: Unlike other `ggplot2` functions, the facet functions do not accept
    unquoted variable names. See the documentation for details._

2. Is there any pattern to the regression lines across the different data sets?

```{r}
dsaur = read.delim("DatasaurusDozen.tsv")
dsaur
```


```{r}
# Your code goes here.
dsaur = read.delim("DatasaurusDozen.tsv")
library(ggplot2)
ggplot(dsaur, aes(dsaur$x, dsaur$y))+geom_point()+facet_wrap(dsaur$dataset)+geom_smooth(method = 'lm')

```

YOUR WRITTEN ANSWER GOES HERE:
Even though the distributions of points in those graph are very different, their regression line have very similar slope. 


Bay Area Apartments Data Set
============================

For the remainder of this lab, you'll continue to analyze the Bay Area
Apartments Data Set introduced in lab 2.

Recall that the Bay Area Apartments Data Set is a collection of 5852
advertisements for apartments for rent in the San Francisco Bay Area. The data
set was collected from Craigslist on Feb 13, 2020.


Exercise 2
----------

Histograms, density plots, and box plots are all good ways to display the
distribution of a 1-dimensional numerical feature. You can use side-by-side box
plots to compare a distribution across the levels of a categorical feature, 

1.  Use `ggplot2` to create side-by-side box plots that show the distribution
    of apartment prices broken down by number of bathrooms. Add descriptive
    labels and a title to your plot.

    _Hint: The `ggplot2` package treats discrete data and categorical data
    differently. You can use the `factor()` function to convert a vector or
    column into categorical data._

2.  Based on your plot, does the number of bathrooms affect the price? If so,
    how?

```{r}
# Your code goes here.
file = readRDS("cl_apartments.rds")
file
```


```{r}
file$bathrooms = factor(file$bathrooms)
ggplot(file, aes(file$bathrooms, file$price))+geom_boxplot() + ggtitle("Price distrition of apartments with different numbers of bathrooms")
```

YOUR WRITTEN ANSWER GOES HERE:
Based on my observation of the plot above, the number of bathrooms does affect the price of apartments in the range of 0-3 bathrooms. In that range, as the number of bathrooms increases, the price of apartments tend to increase as well. 


Exercise 3
----------

Bar plots are a good way to display the distribution (that is, the frequencies)
of a 1-dimensional categorical feature. Groups of bars can be used to compare
against a second categorical feature.

Get the subset of advertisements for apartments with 0 to 3 bedrooms. For the
subset, create a bar plot that shows the frequencies of the different laundry
categories, grouped by the number of bedrooms (on the x-axis). Position the
bars so that they are side-by-side rather than stacked. Add descriptive labels
and a title to your plot.

_Hint: You will need to set the `position` parameter for the geometry layer._

```{r}
# Your code goes here.
small = file[which(file$bedrooms <= 3),]
barplot(table(small$laundry, small$bedrooms),beside = TRUE,xlab = "Number of Bedrooms",ylab="Frequency of Laundries") + title("Distribution of Laundries ")

```

Exercise 4
----------

The `table()` function computes the frequency of each unique value in a vector.
If you want to inspect the distribution of categories in a categorical feature,
the `table()` function is a quick alternative to a bar plot. 

Use the `table()` function to compute a two-way table that shows the number of
bedrooms versus the number of bathrooms for all of the advertisements in
Oakland and San Francisco. Use the `dnn` parameter to label the appropriate
dimensions of the table as "Bedrooms" and "Bathrooms".

Which combination of number of bedrooms and number of bathrooms is most common
among apartment advertisements for these two cities?


```{r}
# Your code goes here.
sfo = file[which(file$city == 'San Francisco' | file$city == 'Oakland'), ]
table(bed, bath)
```

YOUR WRITTEN ANSWER GOES HERE:
Based on the table above, 1b1b is the most common apartment advertisment. 


Exercise 5
----------

Given a vector, the `order()` function returns the vector of positions that
sort the vector if used with the `[` operator. For example, suppose we want to
order this vector from smallest to largest:
```{r}
x = c(4, -6, 21, -2)
```

We can get the ordered vector by calling `order()` and then subsetting:
```{r}
indices = order(x)
indices

x[indices]
```

The `order()` function generalizes to data frames. If you get the ordering for
a column, you can then use the ordering to subset the rows and reorder them.

Use `order()` to find the 5 least expensive apartment advertisements in
Berkeley. Print their price, number of bedrooms, and title. Are all of them ads
for apartments?

```{r}
# Your code goes here.
ids = order(file$price)
print(file$price[ids][0:5])
print(file$bedrooms[ids][0:5])
print(file$title[ids][0:5])
```

YOUR WRITTEN ANSWER GOES HERE:
They are not all ads for apartments. 
